Graph Generators for Data Science: A Survey

### 2018-06-07 generators_general.tex
Added darwini and bter to general graph generators

%\paragraph{gtools} Projects nauty and Traces~\cite{gtools} are programs for computing automorphism groups of graphs and digraphs~\cite{McKay201494}; they can also produce a canonical label. In the respective package there is also suite of programs called gtools which involve generators for non-isomorphic graphs, bipartite graphs, digraphs, and multigraphs.

>>>>

\paragraph{BTER} BTER (Block Two-Level
Erd\"{o}-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
probabilities, connected randomly between them. As a main feature, BTER is able
to reproduce input degree distributions and average clustering
coefficient per degree values. The generators starts by grouping the vertices
by degree $d$, and forming groups of size $d+1$ degree $d$ nodes. Then, these
groups are assigned an internal edge probability in order to match the observed
average clustering coefficient of the nodes of such degree. Based on this
probability, for each node, the excess degree is computed (the degree that in
expectation will not be realized internally in the group) and used to connect
nodes from different groups at random. The authors describe a highly scalable
MapReduce based implementation that is capable of generating large graphs (with
billions of nodes) in reasonable amounts of time.

\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
designed to run on Vertex Centric computing frameworks like
Pregel~\cite{malewicz2010pregel} or Apache Giraph~\cite{ching2015one}, with the
additional feature that it is more accurate when reproducing the clustering
coefficient of the input graph. Instead of just focusing on the average
clustering coefficient for each degree, Darwini is able to model the clustering
coefficient distribution per degree. It achieves this by grouping the vertices
of the graph into buckets by the expected number of closed triangles they need
to close in order to attain the their expected clustering coefficient, which is
sampled from the input distributions. Then, the vertices in each bucket are
connected randomly with a probability that would produce, in expectation, the
desired number of triangles for such bucket. Then, as in BTER, the excess degree
is used to connect the different buckets. The authors report that Darwini is
able to generate graphs with billions and even trillions of edges.

%\paragraph{gtools} Projects nauty and Traces~\cite{gtools} are programs for
%computing automorphism groups of graphs and digraphs~\cite{McKay201494}; they
%can also produce a canonical label. In the respective package there is also
%suite of programs called gtools which involve generators for non-isomorphic
%graphs, bipartite graphs, digraphs, and multigraphs.
